---
title: "Rcpp Modules HOWTO"
author: "Bob Jansen"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Rcpp_Modules_HOWTO}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo = FALSE}
library(RcppModulesExample)
```

# Introduction

The aim of this vignette is to describe all the aspects of Rcpp Modules, from
the very basic to the more advanced. If your not familiar with Rcpp please refer
to Allaire, Eddelbuettel and Francois (2017). Some `C++` knowledge is assumed
but only at a basic level. The author is not a `C++` expert either. Stubbornness
might help. The code does not include any functionality by design. The only goal
of the package is to give minimal examples of all Rcpp Modules features. This
vignette is contained in a fully functional Rcpp package.

The following sections contain a step by step guide of creating the package,
starting with the most basic features.

All steps can be referred to by their own branch, to get to the first step
check out branch `Step1`
```{bash, eval = FALSE}
git checkout Step1
```
and so on. _Branches have not been created yet._

# Step 1: Creating an Rcpp package

If Rcpp is not yet installed, install it. Now you can create a package skeleton
that is ready to use Rcpp with the following command:

```{r, eval = FALSE}
#install.packages('Rcpp')
Rcpp::Rcpp.package.skeleton(
  name = 'RcppModulesExample',
  module = FALSE, # Rcpp comes with some examples as well.
  example_code = FALSE,
  author = "Bob Jansen",
  email = "bobjansen@hey.com"
)
```

